---
title: "p8105 HW5 | Jagjit Singh | UNI: JS5958"
output: github_document
---


# Problem 1
The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r,warning=FALSE, message=FALSE}
library(tidyverse)
full_df = 
  tibble(
    files = list.files("./q1_data/"),
    path = str_c("./q1_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 



# Problem 2

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”): 
```{r}
df = read.csv("q2_data/homicide-data.csv")
homicide_df = df %>% 
  mutate(
    city_state = str_c(city, ', ', state),
    resolution = case_when(
      disposition =="Closed by arrest" ~ "solved",
      disposition =="Closed without arrest" ~ "unsolved",
      disposition =="Open/No arrest" ~"unsolved"
         )) %>% 
  relocate(city_state)



summary_city_df =
  homicide_df %>%
  group_by(city) %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    solved = sum(resolution == "solved"),
    total = n()
    )

summary_city_df
```


Now for the city of Baltimore, MD, we use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe:

```{r}
##### Subset df to baltimore_df
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()) 

statistics_df =
  prop.test(
    x = baltimore_df  %>% pull(unsolved),
    n = baltimore_df  %>% pull(n)) 

statistics_df %>% 
  broom::tidy()
```

```{r}
city_summary  = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution== "unsolved"),
    n = n()
  ) 

tidied_df = city_summary %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

```


```{r}
head(tidied_df)
```


Create a plot that shows the estimates and CIs for each city:

```{r}
library(viridis)
plot = tidied_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point(size = 1, aes(colour = estimate)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 0))

plot
```


# Problem 3

```{r}
sim_n_sd = function(n_obs = 30, mu = 0, sigma = 5) {
  
  data_simulation  = tibble(
    x = rnorm(n = n_obs, mean = mu, sd = sigma)
  )
  
  data_simulation %>%
    summarise(
      mu_hat = mean(x),
      p_value = t.test(x, conf.level = 0.95)$p.value
      )
  
}

```

```{r}
sim_results_df = 
  tibble(mu = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = mu, ~rerun(5000, sim_n_sd(mu = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs) %>%
  mutate(conclusion = ifelse(p_value<0.05, 'reject', 'fail to reject'))

```

Now we make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of $mu$ on the x axis. Describe the association between effect size and power.
```{r}
plot_1 = ggplot(sim_results_df,aes(x = as.factor(mu), fill = conclusion)) + 
  geom_bar(position = "fill") +
  xlab("True mu") + 
  ylab("Proportion")

plot_1
```
From the proportion we can see that possibility of rejecting null hypothesis is directly proportional to value of the true mean for the given set of true means. 

Plot showing the average estimate of mu on the y axis and the true value of mu on the x axis
```{r}
plot_2 = sim_results_df %>%
  group_by(mu) %>%
  summarise_at(vars(mu_hat), list(mu_estimate = mean)) %>%
    ggplot(aes(x = as.factor(mu), y = mu_estimate)) + 
  geom_point() +
  xlab("true value of mu") + ylab("mu estimate")

plot_2
```

```{r}
reject_df = sim_results_df %>%
  filter(conclusion=='reject')

plot_3 =  reject_df  %>%
  group_by(mu) %>%
  summarise_at(vars(mu_hat), list(sample_mean = mean)) %>%
    ggplot(aes(x = as.factor(mu), y = sample_mean)) + 
  geom_point() +
   xlab("true value of mu") + ylab("mu estimate")

plot_3
```

sample average of mu hat across tests for which the null is rejected is not equal to the true mean in most of the cases i.e. for mu = 0,1,2,3. This is because we reject the null hypothesis at alpha = 5%. This implies that we 95% confident that mu hat is not equal to the true population mean. 